Cover Letter

### 2017-12-12 paper/sections/3_posix_overheads.tex
paper: final version
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: popperize all graphs (#27, #28, #37, #40)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{Create-heavy workloads (such as \texttt{untar}) incur the highest disk, network, and
CPU utilization because of the consistency and durability demands of
CephFS.}\label{fig:overhead-creates}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-journal.png}
      \caption{Runtime normalized to no journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.2\linewidth]{graphs/behavior-interfere.png}
      \caption{Interference forces \texttt{lookup()}s}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{Interference hurts variability}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{The overhead of durability and strong consistency in CephFS.
  (a) shows the effect of different journal segment sizes, which are streamed
  into the object store for fault tolerance. (b) and (c) show that when a second
  client ``interferes", capabilities are revoked and metadata servers do more
  work.  \label{fig:overhead}}
\end{figure*}

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}

\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-compile/visualize/viz.ipynb}{source}]
Create-heavy workloads (such as \texttt{untar}) incur the highest disk,
network, and CPU utilization because of the consistency and durability demands
of CephFS.}\label{fig:overhead-creates}

\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=0.95\linewidth]{graphs/slowdown-journal.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-durability/visualize/viz.ipynb}{source}]
      Effect of Journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.1\linewidth]{graphs/behavior-interfere.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-interfere/visualize/viz.ipynb}{source}]
      Interference increases RPCs}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-creates/visualize/viz.ipynb}{source}]
      Interference hurts variability}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{ The overhead of durability and strong consistency in CephFS.  (a)
  shows the effect of different journal segment sizes, normalized to a setup
  without a journal (``No Journal").  The journal is streamed into the object
  store for fault tolerance. (b) and (c) show that when a second client
  ``interferes", capabilities are revoked and metadata servers do more work.
  \label{fig:overhead}}
\end{figure*}

### 2017-12-12 paper/sections/6_results.tex
paper: popperize all graphs (#27, #28, #37, #40)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{Performance of each mechanism (left) and building the
consistency/durability semantics of real-world systems (right) for 100K files
creates from a single client. Results are normalized to the runtime of writing
events to the client's in-memory journal.  \label{fig:composable-mechanisms}}
\end{figure}

@@

{\it Journal Size:} We measure the amount of storage per journal update to be
about 2.5\text{KB}. The storage footprint scales linearly with the number of
metadata creates and suggests that updates for a million files would be 2.5KB
\(*\) 1 million files \(=\) 2.38GB. Transfer times for payloads of this size in
most HPC/data center networks are reasonable.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{Use Case 1} \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{Use Case 2}
      \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{Use Case 3}
      \label{fig:slowdown-sync}
  \end{subfigure}
\caption{The performance and features of Cudele. (a) shows the cost of
merging client journals at the metadata server. Shipping and merging journals of updates scales better than RPCs
because there are less messages and consistency/durability code paths are
bypassed. In (b), the allow/block API isolates directories from interfering
clients. (c) is the slowdown of a single client syncing updates to the global
namespace. The inflection point is the trade-off of frequent updates vs. larger
journal files.\label{fig:use-cases}}
\end{figure*}

@@

This workload scales further with decoupled namespaces because the metadata
server is not overwhelmed with RPC requests. Compared to
Figure~\ref{fig:overhead-c} we can scale to 40 clients which is more than
double the capacity of a single metadata server using the RPC strategy to
maintain strong consistency. Related work has pointed to on-disk metadata
format as the primary factor for improved scalability; but our results show
that the weakened consistency and durability enables the scalability
improvements. The on-disk metadata formats in this experiment are the same for
all schemes.

>>>>

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mechanisms/visualize/viz.ipynb}{source}]
Performance of each mechanism (left) and building the consistency/durability
semantics of real-world systems (right) for 100K files creates from a single
client. Results are normalized to the runtime of writing events to the client's
in-memory journal.  \label{fig:composable-mechanisms}}
\end{figure}

@@

{\it Journal Size:} We measure the amount of storage per journal update to be
about 2.5KB. The storage footprint scales linearly with the number of
metadata creates and suggests that updates for a million files would be 2.5KB
\(*\) 1 million files \(=\) 2.38GB. Transfer times for payloads of this size in
most HPC/data center networks are reasonable.

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mergescale/visualize/viz.ipynb}{source}]
      Use Case 1} \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-blockapi/visualize/viz.ipynb}{source}]
      Use Case 2} \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-partialreads/visualize/viz.ipynb}{source}]
      Use Case 3} \label{fig:slowdown-sync}
  \end{subfigure}
\caption{
The performance and features of Cudele. (a) shows the cost of merging client
journals at the metadata server. Shipping and merging journals of updates
scales better than RPCs because there are less messages and
consistency/durability code paths are bypassed. In (b), the allow/block API
isolates directories from interfering clients. (c) is the slowdown of a single
client syncing updates to the global namespace. The inflection point is the
trade-off of frequent updates vs. larger journal files.\label{fig:use-cases}}
\end{figure*}

@@

This workload scales further with decoupled namespaces because the metadata
server is not overwhelmed with RPC requests. Compared to
Figure~\ref{fig:overhead-c} we can scale to 40 clients which is more than
double the capacity of a single metadata server using the RPC strategy to
maintain strong consistency\footnote{\newcomment{Note that for the 20 clients
bar in Figure~\ref{fig:mergescale}, we plot the throughput for using 18 clients
(the maximum number of clients supported by RPCs)}}. Related work has pointed
to on-disk metadata format as the primary factor for improved scalability; but
our results show that the weakened consistency and durability enables the
scalability improvements. The on-disk metadata formats in this experiment are
the same for all schemes.
